### 2016-01-30 text/MS.Rmd
new version of MS all the way up to half results, tables and figures added

```{r, results="hide", warnings=FALSE, echo=FALSE, message=FALSE}
source('../R/functions-analyses.R')
cleanbib()
myRefs   <-  listBibs()
exporBibs(myRefs, erase=FALSE)
```
**Temperature effects on mass-scaling exponent of metabolic rates: a manipulative test**

@@

Metabolic theory has been lauded as having the potential to unite hierarchical levels of biological organisation `r myCite(c('nisbet2000janimecol', 'brown2004', 'vandermeer2006tree'))`, but definitive tests of the mechanistic theories proposed to underlie the putative link between individual metabolic rate ($B_i$) and ecological patterns remain rare `r myCite('kearney2012amnat')`. Examination of the relationship between $B_i$ and individual body mass, $M_i$, provides an opportunity to test the mechanistic basis of metabolic theory, but manipulative experiments that examine this relationship are also rare `r myCite(c('kearney2012amnat', 'glazier2005biolrev', 'white2013jcompphysb'))`. The relationship between $B_i$ and $M_i$ is typically described by a power function of the form $B_i = B_oM_i^{\alpha}. For most animals, the value of $\alpha$ lies between 0.5 and 1, indicating that individual metabolic rate scales sub-linearly with body mass `r myCite(c('schmidtnielsen1984', 'savage2004', 'glazier2005biolrev'))`. Cross-sectional and longitudinal studies of the intra-specific association between $B_i$ and $M_i$ have revealed that the value of $\alpha$ is associated with many biotic and abiotic variables, including pH `r myCite('vaca2010biollett')`, temperature `r myCite('killen2010ele')`, predation `r myCite('glazier2011ecolmongr')`, inbreeding `r myCite('ketola2012jlinsoc')`, and a range of others (for reviews see `r myCite(c('glazier2005biolrev', 'white2013jcompphysb'))`). Similarly, inter-specific studies have shown that the value of $\alpha$ varies spatially and among taxa (e.g. `r myCite(c('lovegrove2000amnat', 'white2012procb'))`), with metabolic level (e.g. `r myCite('glazier2010biolrev')`), and sometimes with body mass (e.g. `r myCite(c('white2009evolution', 'kolokotrones2010nature'))`). While these intra- and inter-specific studies demonstrate clearly that the value of $\alpha$ is not fixed, they each share a common limitation: each study tests for an association between $\alpha$ and a biotic or abiotic variable, using a value of $\alpha$ that is estimated from the association between $B_i$ and $M_i$ for individuals or species of different size. Such correlative studies cannot address the causal association between $B_i$ and $M_i$, because $M_i$ is correlated with a range of other environmental, physiological, and life history variables (see e.g. `r myCite(c('peters1983', 'calder1984book', 'schmidtnielsen1984'))` for comprehensive reviews) and many of these variables are also associated with $B_i$ `r myCite(c('mcnab2002book', 'konarzewski2013jcompphysb', 'white2013jcompphysb'))`.

In contrast to studies of intact individual organisms, colonial animals provide an opportunity for definitive tests of metabolic theory because colony size can be manipulated experimentally and several metabolic theories predict $\alpha$ explicitly for these animals `r myCite(c('nakaya2005procb', 'white2011amnat', 'kearney2012amnat'))`. The fractal geometry model of West *et al.* `r myCite(c('west1997science', 'west1999science'))`, for example, predicts $\alpha$ on the basis of the transport of essential materials through space-filling outward-directed fractal distribution networks. For an $n$-dimensional organism, this model predicts that $\alpha$ should be equal to $n/(n ‑ 1)$, so a value of $\alpha$ = 0.75 is predicted for three-dimensional animals, and a value of $\alpha$ = 0.67 is predicted for two-dimensional ones `r myCite(c('west1997science', 'west1999science'))` see also `r myCite('koontz2009amjbot')`. However, subsequent work has demonstrated that these canonical predictions of the fractal model are dependent on a range of assumptions `r myCite(c('enquist2009nature', 'savage2008ploscompbiol', 'banavar2010pnas', 'kolokotrones2010nature'))`, and modifications of these can yield exponents that vary between 0.5–-1.0 (e.g. `r myCite('price2007pnas')`). For example, the predicted scaling exponent for a two-dimensional organism with a plane-filling network and area-increasing branching is 0.86 `r myCite('price2007pnas')`. Thus, the fractal model predicts an exponent of either 0.67 `r myCite(c('west1997science', 'west1999science'))` or 0.86 `r myCite('price2007pnas')` for two-dimensional animals, depending on the assumptions used. However, the fractal geometry model makes no predictions about the additional effects of biotic and abiotic variables on the value of $\alpha$, unless these variables have effects on the geometry of the distribution network.

The Dynamic Energy Budget (DEB) theory for metabolic organisation predicts patterns of growth and metabolic scaling on the basis of as generalised surface area (source) and volume (sink) relationships, and predicts the values of both $B_o$ and $\alpha$ during ontogeny on the basis of size-dependent variation in energy allocation to assimilation, maintenance, growth, and maturation `r myCite('kooijman2009book')`. Biotic and abiotic variables can therefore influence the predicted values of $\alpha$ through their effects on these processes. In the case of colonial organisms, DEB theory predicts that biotic and abiotic variables that influence growth rate will have different effects on $\alpha$ for two-dimensional encrusting and three-dimensional arborescent (tree-like) colonies, because patterns of growth differ among these forms. For encrusting colonies, the proportion of growing zooids varies as a function of colony circumference, and therefore scales as $M_i^{\sim 0.5}$. In contrast, the number of growing zooids for arborescent colonies scales as $M_i^{\sim 1}$, because a bifurcating tree with $n$ tips has $n-1$ nodes and a mass proportional to $2n-1$ (Figure 1). Given that the DEB predictions for metabolic scaling in colonial organisms depend upon growth rate and the relative contributions of growing and non-growing zooids to whole-colony metabolism, the utility of the DEB model in predicting variation in $\alpha$ can be tested in two ways. Firstly, because the relative contribution of growing and non-growing zooids to whole-colony metabolism varies with growth rate, which is influenced by temperature, a negative relationship between temperature and $\alpha$ is predicted for two-dimensional encrusting colonies `r myCite(c('white2011amnat', 'kearney2012amnat'))`. Since the normalization of the scaling relationship, $B_o$, will increase with temperature due to the thermodynamic effects of temperature on metabolic rate, this prediction will manifest as a negative association between $\alpha$ and $B_o$. Second, the influence of temperature on the scaling exponent of metabolic rate is predicted to differ among growth forms. This prediction arises because the number of growing tips of an arborescent colony scales as $M_i^{\sim 1}$ (Figure 1), so only the elevation of the relationship between whole-colony metabolic rate and colony mass is predicted to be influenced temperature and no association between between $\alpha$ and $B_o$ is predicted.

In the present study we experimentally test these two explicit predictions of the DEB model for metabolic scaling in colonial organisms by examining the effects of colony form (encrusting or arborescent) and temperature (as a proxy for growth rate) on the scaling of metabolic rate for colonial marine organisms from three phyla (Porifera, Bryozoa [Ectoprocta], and Chordata).

@@

To collect our study organisms, roughened acetate sheets secured to the underside of 6 mm thick PVC sheets suspended from floating pontoons at a depth of 1 m were deployed at Manly Boat Harbour, Queensland, Australia (27˚27' S, 153˚11' E) and checked regularly to remove fouling organisms other than our species of interest. After 6 weeks in the field, sheets bearing colonies were returned to the University of Queensland where they were maintained in aerated seawater for up to 48 h prior to measurements. For encrusting colonies, sections of acetate bearing whole colonies were then cut from the sheets and fragmented (see `r myCite('white2011amnat')` for details and tests of potential experimental artefacts). Arborescent colonies were cut directly from the acetate sheets and fragmented.

The rate of oxygen consumption, $\dot{V}\textrm{O}_\textrm{2}$ of colony fragments was measured at 10 or 25 ˚C using a 144-channel PreSens Sensor Dish Reader (SDR, AS-1 Scientific, Wellington, New Zealand) according to standard techniques `r myCite(c('koster2008meps', 'lighton2008book', 'white2011amnat'))`. $\dot{V}\textrm{O}_\textrm{2}$ was measured by placing the colony or fragment in a glass vial containing 0.2$\mu$m filtered sea water and a non-consumptive $\textrm{O}_\textrm{2}$ sensor spot and calculated from the rate of change of $\textrm{O}_\textrm{2}$ saturation ($m_a$, % h^‑1^) as:

$$\dot{V}\textrm{O}_\textrm{2} = ‑1 \left(\frac{m_a – m_b}{100}\right) V~{\alpha}_{\textrm{O}_\textrm{2}}$$, (1)

where $m_b$ is the rate of change of $\textrm{O}_\textrm{2}$ saturation for blank vials containing no bryozoans (% h^-1^), ${\alpha}_{\textrm{O}_\textrm{2}}$ is the oxygen capacitance of air-saturated sea water at 10 ˚C (6.26 ml l^-1^) or 24 ˚C (4.615 ml l^-1^) `r myCite('cameron1986book')` and $V$ is water volume (chambers were 0.005 l in volume and water volume was calculated by subtracting the volume of acetate and animals). At least four blank vials were recorded simultaneously with each 24-well plate to account for microbial oxygen consumption and sensor spots were calibrated with air-saturated seawater (100 % A.S.) and water containing 2% sodium sulfite (0% A.S.). Following measurement of $\dot{V}\textrm{O}_\textrm{2}$, colonies or fragments were blotted dry and weighed to 0.1 mg (Sartorius A 200 S, Sartorius AG, Göttingen, Germany).  All measurements of \dot{V}\textrm{O}_\textrm{2} were made in one of four dark constant temperature cabinets, with temperatures within a run randomised among cabinets.

To test for the effect of growth form and temperature on the relationship between mass and metabolic rate, we used ANCOVA where mass was the continuous variable, temperature and growth form were categorical variables. When we included experimental conveniences (controlled temperature cabinet and plate(cabinet)) as random factors, these factors and their interactions with our factors of interest were not significant. As they explained little additional variance and were not of biological interest, we omitted them from the final model `r myCite('quinn2002book')`. The scaling exponent, $\alpha$, of the relationship between $\dot{V}\textrm{O}_\textrm{2}$ and fragment mass, $M_i$, was then estimated by ordinary least squares (OLS) linear regression of $\textrm{ln}\dot{V}\textrm{O}_\textrm{2} ~ \textrm{ln}M_i$.

@@

Three-way interaction was significant; within forms there was an interaction between temperature and logM for encrusting colonies, but not arborescent ones.

@@

@@

*Figure 1.* Scaling of the number of the number of tips for a bifurcating arborescent colony with colony mass (expressed relative to the mass of a colony with one tip). Solid line represents isometric scaling of tip number with colony mass.

*Figure 2.* Scaling of rate of oxygen consumption ($\dot{V}\textrm{O}_\textrm{2}, $\mu$l h^-1^) with fragment mass ($M_i$, mg) for size-manipulated fragments of (A) encrusting and (B) arborescent colonial species. Data for *Hippopodina* sp, sponges, *Bugula stolonifera* and *B. neritina* are from the present study; data for *Botrylloides simodensis* and *Hippoporina indica* are from published sources `r myCite(c('nakaya2005procb', 'white2011amnat'))`. Slope and intercept are for the linear ordinary least squares regression relating $\textrm{ln}\dot{V}\textrm{O}_\textrm{2} ~ \textrm{ln}M_i \pm$ SE.

>>>>

```{r, results="hide", warnings=FALSE, echo=FALSE, message=FALSE}
load('../output/RDatafiles/analyses.RData')
load('../output/RDatafiles/numbers.RData')
source('../R/functions-analyses.R')
source('../R/functions-figures.R')
cleanbib()
myRefs   <-  listBibs()
exporBibs(myRefs, erase=TRUE)
```
**Temperature effects on mass-scaling exponent of metabolic rates: a manipulative test**

@@

Metabolic theories have been lauded as having the potential to unite hierarchical levels of biological organisation, from individuals to ecosystems `r myCite(c('nisbet2000janimecol', 'brown2004', 'vandermeer2006tree'))`. Although definitive tests of their underlying assumptions remain rare `r myCite(c('kearney2012amnat', 'newberry2015ploscomputbiol'))`, myriad studies examined their predictions with regards to the relationship between individual level metabolic rates, $B_i$, and individual body mass, $M_i$ `r myCite(c('kleiber1932', 'kleiber1961', 'peters1983', 'schmidtnielsen1984', 'glazier2005biolrev', 'delong2010', 'glazier2010biolrev'))`. The relationship between $B_i$ and $M_i$ is typically described by a power function of the form $B_i = B_oM_i^{\alpha}$, where $B_o$ is a normalisation constant independent of mass and $\alpha$ is a dimensionless scaling exponent. For most animals, individual metabolic rate scales sub-linearly with body mass, with $\alpha$ estimates falling between 0.5 and 1, and averaging around 0.75 `r myCite(c('kleiber1961', 'savage2004', 'glazier2005biolrev', 'delong2010'))`. Metabolic rates are also influenced by temperature. Two prevalent competing metabolic theories, the fractal geometry model `r myCite(c('west1997science', 'west1999science'))`, and  the Dynamic Energy Budget (DEB) theory for metabolic organisation `r myCite('kooijman2009book')`, provide opposing views on the role of temperature on metabolic rates and the relationship between the mass scaling of metabolic rates and temperature: the former assumes that temperature affects the metabolic normalisation only `r myCite('gillooly2001')`, i.e. mass-scaling and temperature dependence are independent; contrarily, the latter predicts changing relationships between mass scaling and temperature dependence through the effects of temperature on assimilation, maintenance, growth, and maturation `r myCite('kooijman2009book')`.

Empirical studies of the intra-specific association between $B_i$ and $M_i$ have revealed that the value of $\alpha$ is associated with many biotic and abiotic variables, including pH `r myCite('vaca2010biollett')`, temperature `r myCite('killen2010ele')`, predation `r myCite('glazier2011ecolmongr')`, inbreeding `r myCite('ketola2012jlinsoc')`, and a range of others (for reviews see `r myCite(c('glazier2005biolrev', 'white2013jcompphysb'))`). Similarly, inter-specific studies have shown that the value of $\alpha$ varies among taxa and/or locations (e.g. `r myCite(c('lovegrove2000amnat', 'white2012procb', 'barneche2014ele'))`), with metabolic level (e.g. `r myCite('glazier2010biolrev')`), and sometimes with body mass (e.g. `r myCite(c('white2009evolution', 'kolokotrones2010nature'))`). While these intra- and inter-specific studies demonstrate clearly that the value of $\alpha$ is not fixed, they each share a common limitation: each study tests for an association between $\alpha$ and a biotic or abiotic variable, using a value of $\alpha$ that is estimated from the association between $B_i$ and $M_i$ for individuals or species of different size. Such correlative studies cannot address the causal association between $B_i$ and $M_i$, because $M_i$ is correlated with a range of other environmental, physiological, and life history variables (see e.g. `r myCite(c('peters1983', 'calder1984book', 'schmidtnielsen1984'))` for comprehensive reviews) and many of these variables are also associated with $B_i$ `r myCite(c('mcnab2002book', 'konarzewski2013jcompphysb', 'white2013jcompphysb'))`.

In contrast to studies that make use of intact individual organisms, colonial animals provide an opportunity for definitive tests of metabolic theories. Colony size can be manipulated experimentally, hence allowing for the potential to remove the confounding effects of body size and life-history traits (e.g. `r myCite('white2011amnat')`). Furthermore, different colonial species may grow in different dimensions, and the mass-scaling exponent $\alpha$ is explicitly predicted to change with number of body dimensions `r myCite(c('nakaya2005procb', 'white2011amnat', 'kearney2012amnat'))`. For example, the fractal geometry model `r myCite(c('west1997science', 'west1999science'))` predicts that $\alpha = n/(n + 1)$ for a $n$-dimensional organism, hence a value of $\alpha$ = 0.75 is predicted for three-dimensional animals while a value of $\alpha$ = 0.67 is predicted for two-dimensional animals (but see `r myCite(c('enquist2009nature', 'savage2008ploscompbiol', 'banavar2010pnas', 'kolokotrones2010nature', 'price2007pnas', 'koontz2009amjbot'))`). On the other hand, DEB predicts that metabolic scaling in colonial organisms are dependent upon growth rate (which is in turn influenced by temperature) and the relative contributions of growing and non-growing zooids to whole-colony metabolism.

In the present study we experimentally manipulate size in different colonial marine organisms from two phyla (Bryozoa [Ectoprocta] and Porifera) in order to test whether the mass scaling and temperature dependence of metabolic rates interact `r myCite(c('white2011amnat', 'kearney2012amnat'))`. In doing so, we explicitly test if these interactions are general or species specific.

@@

*1. Animal collections*  
To collect our study organisms, roughened acetate sheets secured to the underside of 6 mm thick PVC sheets suspended from floating pontoons at a depth of 1 m were deployed at Manly Boat Harbour, Queensland, Australia (27˚27' S, 153˚11' E) and checked regularly to remove fouling organisms other than our species of interest: *Bugula neritina* and *B. stolonifera* (arborescent bryozoan), *Hippopodina* sp. (encrusting bryozoan), and an unidentified species of sponge belonging to the Microcionidae family `r myCite('hart2009ecology')` (Table 1). After 6 weeks in the field, sheets bearing colonies were returned to the University of Queensland where they were maintained in aerated seawater for up to 48 h prior to measurements. For encrusting colonies, sections of acetate bearing whole colonies were then cut from the sheets and fragmented (see `r myCite('white2011amnat')` for details and tests of potential experimental artefacts). Arborescent colonies were cut directly from the acetate sheets and fragmented.

*2. Respiration measurements*  
Individual metabolic rates (**provide units**, *n* = `r nrow(metRates)`), $B_i$, were measured as rate of oxygen consumption, $\dot{V}\textrm{O}_\textrm{2}$ of colony fragments was measured at 10 or 25 ˚C using a 144-channel PreSens Sensor Dish Reader (SDR, AS-1 Scientific, Wellington, New Zealand) according to standard techniques `r myCite(c('koster2008meps', 'lighton2008book', 'white2011amnat'))`. $\dot{V}\textrm{O}_\textrm{2}$ was measured by placing the colony or fragment in a glass vial containing 0.2$\mu$m filtered sea water and a non-consumptive $\textrm{O}_\textrm{2}$ sensor spot and calculated from the rate of change of $\textrm{O}_\textrm{2}$ saturation ($m_a$, % h^‑1^) as:

$$\dot{V}\textrm{O}_\textrm{2} = ‑1 \left(\frac{m_a – m_b}{100}\right) V~{\beta}_{\textrm{O}_\textrm{2}}$$, (1)

where $m_b$ is the rate of change of $\textrm{O}_\textrm{2}$ saturation for blank vials containing no bryozoans (% h^-1^), ${\beta}_{\textrm{O}_\textrm{2}}$ is the oxygen capacitance of air-saturated sea water at 10 ˚C (6.26 ml l^-1^) or 24 ˚C (4.615 ml l^-1^) [**double-check these numbers. Shouldn't the second be 25 ˚C?**] `r myCite('cameron1986book')` and $V$ is water volume (chambers were 0.005 l in volume and water volume was calculated by subtracting the volume of acetate and animals). At least four blank vials were recorded simultaneously with each 24-well plate to account for microbial oxygen consumption and sensor spots were calibrated with air-saturated seawater (100 % A.S.) and water containing 2% sodium sulfite (0% A.S.). Following measurement of $\dot{V}\textrm{O}_\textrm{2}$, colonies or fragments were blotted dry and weighed to 0.1 mg (Sartorius A 200 S, Sartorius AG, Göttingen, Germany). All measurements of $\dot{V}\textrm{O}_\textrm{2}$ were made in one of four dark constant temperature cabinets, with temperatures within a run randomised among cabinets.

*3. Statistical analyses*  
To test for the interacting effects of body mass and temperature on metabolic rate across species, we fitted a three-way interaction linear model using log-transformed data

$$\textrm{ln}B_i \sim \textrm{ln}M_i * Temperature * Species$$, (2)

where mass (mg), $\textrm{ln}M_i$, is a continuous variable, while temperature (two levels: 10 ˚C and 25 ˚C) and species (four levels corresponding to the four species) are categorical variables. With this model, we allow each species to have a different mass-scaling slope that may change with temperature (4 $\times$ 2 = 8 parameters); it also accounts for species- and temperature-specific deviations on the metabolic normalisation (i.e. statistical model intercept; 4 $\times$ 2 = 8 parameters). We also included experimental conveniences (plate reader, $\Delta P_r$, and date, $\Delta D$) as random effects on the metabolic normalisation to help control for natural experimental variability (3 additional hyper parameters corresponding to the standard deviation of $\Delta P_r$, $\Delta D$ and random-effects residual).

We then performed a model selection by comparing the statistical model in equation 2 with a simpler two-way interaction model of similar structure,

$$\textrm{ln}B_i \sim \textrm{ln}M_i * Temperature + Species$$. (3)

In this model, different from the model in equation 2, the mass scaling slope is no longer allowed to vary across different species, but is still allowed to vary between different temperatures (1 $\times$ 2 = 2 parameters). The metabolic normalisation, however, is still allowed to vary across species (4 $\times$ 1 = 4 parameters) and between temperatures (1 additional parameters), and random effects were maintained (i.e. 3 hyper parameters). Equation 3 represents a statistical model nested in the model represented by equation 2, and therefore their performance can be directly assessed `r myCite('zuur2009book')`. Such comparison allowed us to formally test our main hypothesis of significant mass-temperature interactions across different species.

Both models were fitted in a Bayesian framework by calling *JAGS* version 3.4.0 from the R package *R2jags* version 0.05-03 `r myCite('r2jags')` in order to derive posterior distributions and associated 95% credible intervals (CIs) for the fitted parameters. Random effects were assumed to be normally distributed, with means of 0. Fitted parameters were assigned priors that were vague (i.e. locally uniform over the region supported by the likelihood) `r myCite('kruschke2014book')`. The posterior distributions of model parameters were estimated using Markov chain Monte Carlo (MCMC) methods by constructing three chains of 500,000 steps each. Chains were thinned using a 250-step interval, so a total of 6,000 steps were retained to estimate posterior distributions (i.e. 3 $\times$ 500,000/250 = 6,000). Models were compared adopting Deviance information criterion (DIC), which are commonly used in Bayesian model selection and are analogously similar to the Akaike information criterion (AIC), as this method also penalises for additional model parameters `r myCite('hooten2015ecology')`. We adopted a conservative approach, and models were considered significantly different only if DIC units differed by > 10 units `r myCite('spiegelhalter2002jrss')`. All data and code necessary to reproduce this paper, its analyses, tables and figures can be obtained on GitHub https://github.com/dbarneche/MTRBrEs.

@@

Our model selection approach indicated that the three-way interaction model (equation 2) performed significantly better than the two-way interaction model (equation 3) ($\Delta$d.f. = `r deltaDF`; $\Delta$DIC = `r rounded(deltaDIC)`), thus implying that different species present different interactions between mass-scaling and temperature dependence. Particularly, the best model yields no interaction between mass scaling and temperature dependence for *Bugula stolonifera* and the Microcionidae sponge (large overlap between 95% credible  intervals). On the other hand, *Bugula neritina* and *Hippopodina* sp. present opposing interactions (Figure 1). For example, parameter estimates indicate that the difference in metabolic rates between 25 ˚C and 10 ˚C for *Hippopodina* sp. decreases `r rounded(tempDeltas[1,'tempDelta'])`-fold moving from `r round(exp(2))` to `r round(exp(5))` mg. On the other hand, rates increase `r rounded(1/tempDeltas[3,'tempDelta'])`-fold along the same body-mass gradient for *Bugula neritina*.

**Compare model estimates with WBE and DEB predictions?**

@@

**Tables**

*Table 1.* Mass ranges and sampling efforts for the four species of Bryozoa and Porifera experimentally manipulated in the present study at two extreme temperatures.

@@

*Figure 1.* Estimates from the three-way interaction model as obtained by Bayesian methods in *JAGS*. Results for each species are represented in groups of four plots, with blue and red colours representing actual data and parameter estimates at 10 ˚C and 25 ˚C, respectively. *Top-left*: posterior distributions of mass-scaling exponents, with horizontal bars representing 95% credible intervals. *Bottom-right*: posterior distributions of metabolic normalisations, with vertical bars representing 95% credible intervals. *Bottom-left*: covariance between mass-scaling exponents and metabolic normalisations for each of the 6,000 MCMC iterations (translucent circles), with overlaid density heat-map. *Top-right*: regressions of individual metabolic rate, $\textrm{ln}B_i$, as functions of individual body mass, $\textrm{ln}M_i$. Regression fits were plotted using the average from the posterior distributions. In  probability posterior plots (top-left and bottom-right), smooth probability curves were approximated from the posterior density curves using very small bins (see electronic supplementary material).
